cvx-flats

### 2020-05-20 neurips-20/cvx-flats-statements.tex
tweaks

\begin{theorem}
  \label{thm:bayes-risk-lower-bound}
  Let $L$ elicit some identifiable $\Gamma:\simplex\to\reals^d$ with $\iden(\Gamma)=d$.
  If $\lbar$ is non-constant on every non-singleton level set of $\Gamma$, then $\eliccvx(\lbar) \geq d+1$.
\end{theorem}
\begin{proof}
  Suppose for a contradiction that we have some convex-elicitable property $\hat\Gamma:\simplex\to\reals^d$ and link $\psi : \reals^d \to \reals$ such that $\lbar = \psi \circ \hat\Gamma$.
  The condition $\elic_\I(\Gamma)=d$ implies that $\Gamma$ is $d$-identifiable but not $(d-1)$-identifiable, and thus there must be some level set $\Gamma_r$ which is a flat of dimension $n-d-1$.

@@

  By Theorem~\ref{thm:cvx-flats}, as $\hat\Gamma$ is $d$-convex elicitable $\hat\Gamma_{\hat r}$ is the union of flats of dimension $n-d-1$ interesected with $\simplex$.
  \raft{Should flesh out this next step; this is the key step}
  As $\hat\Gamma_{\hat r} \subseteq \Gamma_r$ and $\Gamma_r$ is a flat of dimension $n-d-1$ interesected with $\simplex$, we conclude $\hat\Gamma_{\hat r} = \Gamma_r$.
  Since by assumption $\lbar$ is non-constant on $\Gamma_r = \hat\Gamma_{\hat r}$, we have distributions $p,p' \in\hat\Gamma_{\hat r}$ with $\lbar(p)\neq\lbar(p')$, which again contradicts $\lbar = \psi \circ \hat\Gamma$.
\end{proof}

>>>>

\begin{theorem}
  \label{thm:bayes-risk-lower-bound}
  Let $L$ elicit some identifiable $\Gamma:\simplex\to\reals^d$ with $\iden(\Gamma)=d$.
  If $\lbar$ is non-constant on every non-singleton level set of $\Gamma$, then $\eliccvx(\lbar) \geq \min(d+1,n-1)$.
\end{theorem}
\begin{proof}
  Suppose for a contradiction that we have some convex-elicitable property $\hat\Gamma:\simplex\to\reals^d$ and link $\psi : \reals^d \to \reals$ such that $\lbar = \psi \circ \hat\Gamma$.
  The condition $\elic_\I(\Gamma)=d$ implies that $\Gamma$ is $d$-identifiable but not $(d-1)$-identifiable, and thus there must be some level set $\Gamma_r$ which is a flat of dimension $n-d-1$.
  \raft{What I mean is you can't describe $\Gamma_r$ using a flat of another dimension; revisit once we settle terminology}

@@

  By Theorem~\ref{thm:cvx-flats}, as $\hat\Gamma$ is $d$-convex elicitable $\hat\Gamma_{\hat r}$ is the union of flats of dimension $n-d-1$ interesected with $\simplex$.
  \raft{Should flesh out this next step; this is the key step}
  As $\hat\Gamma_{\hat r} \subseteq \Gamma_r$ and $\Gamma_r$ is a flat of dimension $n-d-1$ interesected with $\simplex$, we conclude $\hat\Gamma_{\hat r} = \Gamma_r$.
  Since by assumption $\lbar$ is non-constant on $\Gamma_r = \hat\Gamma_{\hat r}$, we have distributions $p,p' \in\hat\Gamma_{\hat r}$ with $\lbar(p)\neq\lbar(p')$, which again contradicts $\lbar = \psi \circ \hat\Gamma$.
  \raft{We actually needed $\Gamma_r$ to be a non-singleton for this last step; otherwise we need to conclude the $n-1$ case; revisit after flat/dimension stuff}
\end{proof}
